---
title: "KNN"
author: "Connor Cabrey"
date: "2022-12-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(class)
library(ggplot2)
library(GGally)
library(janitor)
library(caret)
```

Importing in training/testing data and mutating variables to as.numeric.  Factors introduce NA coercion with KNN.
```{r}
H1B_Test <- read_csv(file = "../Data/H1B_Test.csv")
H1B_Train <- read_csv(file = "../Data/H1B_Train.csv")

H1B_Train <- H1B_Train %>% 
  mutate(CASE_STATUS = as.factor(CASE_STATUS),
         CASE_STATUS = as.numeric(CASE_STATUS),
         PW_SKILL_LEVEL = as.factor(PW_SKILL_LEVEL),
         PW_SKILL_LEVEL = as.numeric(PW_SKILL_LEVEL),
         WAGE_OFFER_UNIT_OF_PAY = as.factor(WAGE_OFFER_UNIT_OF_PAY),
         WAGE_OFFER_UNIT_OF_PAY = as.numeric(WAGE_OFFER_UNIT_OF_PAY),
         MINIMUM_EDUCATION = as.factor(MINIMUM_EDUCATION),
         MINIMUM_EDUCATION = as.numeric(MINIMUM_EDUCATION),
         REQUIRED_EXPERIENCE = as.factor(REQUIRED_EXPERIENCE),
         REQUIRED_EXPERIENCE = as.numeric(REQUIRED_EXPERIENCE),
         ACCEPT_ALT_OCCUPATION = as.factor(ACCEPT_ALT_OCCUPATION),
         ACCEPT_ALT_OCCUPATION = as.numeric(ACCEPT_ALT_OCCUPATION),
         FOREIGN_LANGUAGE_REQUIRED = as.factor(FOREIGN_LANGUAGE_REQUIRED),
         FOREIGN_LANGUAGE_REQUIRED = as.numeric(FOREIGN_LANGUAGE_REQUIRED),
         PROFESSIONAL_OCCUPATION = as.factor(PROFESSIONAL_OCCUPATION),
         PROFESSIONAL_OCCUPATION = as.numeric(PROFESSIONAL_OCCUPATION),
         COUNTRY_OF_CITIZENSHIP = as.factor(COUNTRY_OF_CITIZENSHIP),
         COUNTRY_OF_CITIZENSHIP = as.numeric(COUNTRY_OF_CITIZENSHIP),
         CLASS_OF_ADMISSION = as.factor(CLASS_OF_ADMISSION),
         CLASS_OF_ADMISSION = as.numeric(CLASS_OF_ADMISSION),
         FOREIGN_WORKER_EDUCATION = as.factor(FOREIGN_WORKER_EDUCATION),
         FOREIGN_WORKER_EDUCATION = as.numeric(FOREIGN_WORKER_EDUCATION),
         FOREIGN_WORKER_ED_INST_US = as.factor(FOREIGN_WORKER_ED_INST_US),
         FOREIGN_WORKER_ED_INST_US = as.numeric(FOREIGN_WORKER_ED_INST_US),
         FOREIGN_WORKER_REQ_EXPERIENCE = as.factor(FOREIGN_WORKER_REQ_EXPERIENCE),
         FOREIGN_WORKER_REQ_EXPERIENCE = as.numeric(FOREIGN_WORKER_REQ_EXPERIENCE),
         FOREIGN_WORKER_EXP_WITH_EMPL = as.factor(FOREIGN_WORKER_EXP_WITH_EMPL),
         FOREIGN_WORKER_EXP_WITH_EMPL = as.numeric(FOREIGN_WORKER_EXP_WITH_EMPL),
         FOREIGN_WORKER_CURR_EMPLOYED = as.factor(FOREIGN_WORKER_CURR_EMPLOYED),
         FOREIGN_WORKER_CURR_EMPLOYED = as.numeric(FOREIGN_WORKER_CURR_EMPLOYED),
         EMPLOYER_COMPLETED_APPLICATION = as.factor(EMPLOYER_COMPLETED_APPLICATION),
         EMPLOYER_COMPLETED_APPLICATION = as.numeric(EMPLOYER_COMPLETED_APPLICATION))

H1B_Test <- H1B_Test %>% 
  mutate(CASE_STATUS = as.factor(CASE_STATUS),
         CASE_STATUS = as.numeric(CASE_STATUS),
         PW_SKILL_LEVEL = as.factor(PW_SKILL_LEVEL),
         PW_SKILL_LEVEL = as.numeric(PW_SKILL_LEVEL),
         WAGE_OFFER_UNIT_OF_PAY = as.factor(WAGE_OFFER_UNIT_OF_PAY),
         WAGE_OFFER_UNIT_OF_PAY = as.numeric(WAGE_OFFER_UNIT_OF_PAY),
         MINIMUM_EDUCATION = as.factor(MINIMUM_EDUCATION),
         MINIMUM_EDUCATION = as.numeric(MINIMUM_EDUCATION),
         REQUIRED_EXPERIENCE = as.factor(REQUIRED_EXPERIENCE),
         REQUIRED_EXPERIENCE = as.numeric(REQUIRED_EXPERIENCE),
         ACCEPT_ALT_OCCUPATION = as.factor(ACCEPT_ALT_OCCUPATION),
         ACCEPT_ALT_OCCUPATION = as.numeric(ACCEPT_ALT_OCCUPATION),
         FOREIGN_LANGUAGE_REQUIRED = as.factor(FOREIGN_LANGUAGE_REQUIRED),
         FOREIGN_LANGUAGE_REQUIRED = as.numeric(FOREIGN_LANGUAGE_REQUIRED),
         PROFESSIONAL_OCCUPATION = as.factor(PROFESSIONAL_OCCUPATION),
         PROFESSIONAL_OCCUPATION = as.numeric(PROFESSIONAL_OCCUPATION),
         COUNTRY_OF_CITIZENSHIP = as.factor(COUNTRY_OF_CITIZENSHIP),
         COUNTRY_OF_CITIZENSHIP = as.numeric(COUNTRY_OF_CITIZENSHIP),
         CLASS_OF_ADMISSION = as.factor(CLASS_OF_ADMISSION),
         CLASS_OF_ADMISSION = as.numeric(CLASS_OF_ADMISSION),
         FOREIGN_WORKER_EDUCATION = as.factor(FOREIGN_WORKER_EDUCATION),
         FOREIGN_WORKER_EDUCATION = as.numeric(FOREIGN_WORKER_EDUCATION),
         FOREIGN_WORKER_ED_INST_US = as.factor(FOREIGN_WORKER_ED_INST_US),
         FOREIGN_WORKER_ED_INST_US = as.numeric(FOREIGN_WORKER_ED_INST_US),
         FOREIGN_WORKER_REQ_EXPERIENCE = as.factor(FOREIGN_WORKER_REQ_EXPERIENCE),
         FOREIGN_WORKER_REQ_EXPERIENCE = as.numeric(FOREIGN_WORKER_REQ_EXPERIENCE),
         FOREIGN_WORKER_EXP_WITH_EMPL = as.factor(FOREIGN_WORKER_EXP_WITH_EMPL),
         FOREIGN_WORKER_EXP_WITH_EMPL = as.numeric(FOREIGN_WORKER_EXP_WITH_EMPL),
         FOREIGN_WORKER_CURR_EMPLOYED = as.factor(FOREIGN_WORKER_CURR_EMPLOYED),
         FOREIGN_WORKER_CURR_EMPLOYED = as.numeric(FOREIGN_WORKER_CURR_EMPLOYED),
         EMPLOYER_COMPLETED_APPLICATION = as.factor(EMPLOYER_COMPLETED_APPLICATION),
         EMPLOYER_COMPLETED_APPLICATION = as.numeric(EMPLOYER_COMPLETED_APPLICATION))


```



Creating my Xtrain, Ytrain, Xtext, Ytest dataframes/vectors for creating of my knn model
```{r}
Xtrain <- H1B_Train  %>% 
  dplyr::select(-c(...1, CASE_STATUS))# Our training set X

Ytrain  <-  H1B_Train$CASE_STATUS

Xtest = H1B_Test  %>% 
  dplyr::select(-c(...1, CASE_STATUS))

Yhat <- knn(Xtrain, Xtest, Ytrain, k = 10, prob = T) 

Ytest <- H1B_Test$CASE_STATUS
```

Getting our confusion matrix for the k=10 run
```{r}
conf_matrix <- table(Ytest, Yhat)
conf_matrix
```

Classification rate for k = 10
```{r}
class_rate <- (624 + 662) / (662+ 624 + 125 + 94)
mis_class_rate <- 1-class_rate
mis_class_rate
```

Graphing K's from 1-100 and getting the minimum error rate k
```{r}
# Initialize data
err_class <- rep(1:100)
tpr <- rep(1:100)
fpr <- rep(1:100)

# run the loop
for (k in 1:100){
  Yhat <- knn(Xtrain, Xtest, Ytrain, k = k) 
  err_class[k] <- mean(Yhat != Ytest) # The prediction is not correct
  tpr[k] <- sum(Yhat == 2 & Ytest == 2) / sum(Ytest == 2) # TP/P
  fpr[k] <- sum(Yhat == 2 & Ytest == 1) / sum(Ytest == 1) # FP/N
}

ggplot(tibble(err_class, k = 1:100), aes(x = k, y = err_class)) +
  geom_line()
```

```{r}
#Getting Smallest Error Rate
which.min(err_class) # gives the k
err_class[which.min(err_class)] # Probability of a Mis-classification 
```

Getting our Y-hat's for the most optimal k of 7
```{r}
#Running with Best K
Yhat_7 <- knn(Xtrain, Xtest, Ytrain, k = 7, prob = T) 

```

Confusion matrix for k = 7
```{r}
#Confusion Matrix
conf_matrix <- table(Ytest, Yhat_7)
conf_matrix
```

Classfication Rate and Missclassification Rate for our ideal k
```{r}
#Calculating Missclassification Rate for our ideal K

class_rate = (table(Ytest, Yhat_7)[1, 1] + table(Ytest, Yhat_7)[2, 2])/(1505)

#Misclassification Rate is 1-Classification Rate
1-class_rate
```

Testing the model's ability to predict
```{r}
#Using Yuka and Connie as tests

H1B_Test_Us <- read_csv(file = "../Data/H1B_Test_us.csv")

H1B_Test_Us <- H1B_Test_Us %>% 
  mutate(PW_SKILL_LEVEL = as.factor(PW_SKILL_LEVEL),
         PW_SKILL_LEVEL = as.numeric(PW_SKILL_LEVEL),
         WAGE_OFFER_UNIT_OF_PAY = as.factor(WAGE_OFFER_UNIT_OF_PAY),
         WAGE_OFFER_UNIT_OF_PAY = as.numeric(WAGE_OFFER_UNIT_OF_PAY),
         MINIMUM_EDUCATION = as.factor(MINIMUM_EDUCATION),
         MINIMUM_EDUCATION = as.numeric(MINIMUM_EDUCATION),
         REQUIRED_EXPERIENCE = as.factor(REQUIRED_EXPERIENCE),
         REQUIRED_EXPERIENCE = as.numeric(REQUIRED_EXPERIENCE),
         ACCEPT_ALT_OCCUPATION = as.factor(ACCEPT_ALT_OCCUPATION),
         ACCEPT_ALT_OCCUPATION = as.numeric(ACCEPT_ALT_OCCUPATION),
         FOREIGN_LANGUAGE_REQUIRED = as.factor(FOREIGN_LANGUAGE_REQUIRED),
         FOREIGN_LANGUAGE_REQUIRED = as.numeric(FOREIGN_LANGUAGE_REQUIRED),
         PROFESSIONAL_OCCUPATION = as.factor(PROFESSIONAL_OCCUPATION),
         PROFESSIONAL_OCCUPATION = as.numeric(PROFESSIONAL_OCCUPATION),
         COUNTRY_OF_CITIZENSHIP = as.factor(COUNTRY_OF_CITIZENSHIP),
         COUNTRY_OF_CITIZENSHIP = as.numeric(COUNTRY_OF_CITIZENSHIP),
         CLASS_OF_ADMISSION = as.factor(CLASS_OF_ADMISSION),
         CLASS_OF_ADMISSION = as.numeric(CLASS_OF_ADMISSION),
         FOREIGN_WORKER_EDUCATION = as.factor(FOREIGN_WORKER_EDUCATION),
         FOREIGN_WORKER_EDUCATION = as.numeric(FOREIGN_WORKER_EDUCATION),
         FOREIGN_WORKER_ED_INST_US = as.factor(FOREIGN_WORKER_ED_INST_US),
         FOREIGN_WORKER_ED_INST_US = as.numeric(FOREIGN_WORKER_ED_INST_US),
         FOREIGN_WORKER_REQ_EXPERIENCE = as.factor(FOREIGN_WORKER_REQ_EXPERIENCE),
         FOREIGN_WORKER_REQ_EXPERIENCE = as.numeric(FOREIGN_WORKER_REQ_EXPERIENCE),
         FOREIGN_WORKER_EXP_WITH_EMPL = as.factor(FOREIGN_WORKER_EXP_WITH_EMPL),
         FOREIGN_WORKER_EXP_WITH_EMPL = as.numeric(FOREIGN_WORKER_EXP_WITH_EMPL),
         FOREIGN_WORKER_CURR_EMPLOYED = as.factor(FOREIGN_WORKER_CURR_EMPLOYED),
         FOREIGN_WORKER_CURR_EMPLOYED = as.numeric(FOREIGN_WORKER_CURR_EMPLOYED),
         EMPLOYER_COMPLETED_APPLICATION = as.factor(EMPLOYER_COMPLETED_APPLICATION),
         EMPLOYER_COMPLETED_APPLICATION = as.numeric(EMPLOYER_COMPLETED_APPLICATION)) %>% 
  dplyr::select(-c(...1))

us_pred <- knn(Xtrain, as.tibble(H1B_Test_Us), Ytrain, k = 7, prob = T) 
```




